---
title: "Database Round Up Oxycodone"
author: 'Palmer Lab: Bonnie Lin'
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
# setwd("~/Dropbox (Palmer Lab)/Palmer Lab/Bonnie Lin/github/Olivier_U01Oxycodone/QC")
# olivier_oxycodone_genotyping <- flowcell_df %>% left_join(., WFU_OlivierOxycodone_test_df[, c("cohort", "rfid")], by = "rfid") %>% subset(!is.na(cohort)) ## add source, consider reorganization source("~/Palmer\ Lab/Bonnie\ Lin/github/PalmerLab_genotyping/CREATE/EXTRACT_SAMPLEBARCODELIBRARY.R") # should work... might not bc it doesn't have dropbox in path
# save(WFU_OlivierOxycodone_test_df, date_time_subject_df_comp, olivieroxy_excel, rat_info_allcohort_xl_df, olivier_spleens_df, olivier_oxycodone_genotyping, file = "Olivier_oxy_data.RData")
load(file = "Olivier_oxy_data.RData")
```

## For Olivier George

Below, you will find the number of records that I have for your experiments, broken down by cohorts.


### \# of IDs from Wake Forest shipment sheets

```{r wfu-master, echo = F}
WFU_OlivierOxycodone_test_df %>% select(cohort) %>% table()
```

### \# of subjects in raw data

These were extracted from the text files in */GWAS (1)/Oxycodone/Oxycodone GWAS*

```{r raw-data, echo = F}
date_time_subject_df_comp %>% 
  distinct(labanimalid, cohort) %>% 
  select(cohort) %>% table()
```

### \# of subjects in excel data

These were extracted from the Excel sheets in *Olivier_George_U01/GWAS Self Administration Data/Oxy Data*

```{r xl-data, echo = F}
olivieroxy_excel %>% 
  mutate(cohort = paste0("C", as.character(parse_number(cohort)) %>% str_pad(2, "left", "0"))) %>% 
  distinct(cohort, labanimalid) %>% select(cohort) %>% table()
```

### \# of subjects with weight data

These were extracted from the Excel sheets in *Olivier_George_U01/Rat Information/Oxycodone*

```{r weights, echo = F}
rat_info_allcohort_xl_df %>% 
  distinct(cohort, rfid) %>% 
  select(cohort) %>% table()
```

### \# of IDs from tissue shipments

Spleens
```{r, echo = F}
olivier_spleens_df %>% 
  subset(experiment == "Oxy") %>% 
  select(cohort) %>% table()
```


### \# of subjects in genotyping pipeline

This is the number of animals we are currently genotyping. 

```{r genotyped, echo = F}
olivier_oxycodone_genotyping %>% distinct(rfid, cohort) %>% 
  mutate(cohort = paste0("C", cohort)) %>% 
  select(cohort) %>% table()
```